Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-06-25 WholePlotTrajectories.Rmd
relecture

The large areas covered with tropical forests worldwide hold crucial environmental, economic and social values. 
They provide wood and multiple non-timber forest products, shelter a diversified fauna, regulate the local climate, and the carbon, water and nutrient cycles, and ensure cultural and human well-being. 
The growing demand in forests products together with current climatic changes increases the pressure on remaining forests [@Gibson2011a; @Morales-Hidalgo2015]and threatens the maintenance and dynamics in space and time of communities structure, composition and functioning [@Anderson-Teixeira2013;@Sist2015].

>>>>

The large areas covered with tropical forests worldwide hold crucial environmental, economic and social values. 
They provide wood and multiple non-timber forest products, shelter a diversified fauna, regulate the local climate, and the carbon, water and nutrient cycles, and ensure cultural and human well-being. 
The growing demand in forests products together with current climatic changes increases the pressure on remaining forests [@Gibson2011a; @Morales-Hidalgo2015] and threatens the maintenance and dynamics in space and time of communities structure, composition and functioning [@Anderson-Teixeira2013;@Sist2015].
